Effects of Solid State Drives on Database Performance

### 2017-04-12 term_paper/paper.tex
More references, more paragraphs.

Text goes here.

@@

Text goes here.

>>>>

There are also a number of software improvements that can be made to take advantage of what flash-based storage is good 
at and helping to mitigate what they are bad at, much like what current filesystem drivers have done with magnetic media.

Operating systems file drivers will need to become aware of flash-based media. We have seen this recently, for example, 
with Apple's introduction of the Apple File System (APFS). It promises to bring with it a number improvements, most notably
in the case of this papaer, being optimized to work with flash-based storage. \cite{AppleComputer2017}

Systems that are data-heavy will need to attempt to optimize their access patterns for SSDs rather than HDDs.

@@

Overall, solid state drives are a huge performance improvement over rotational magnetic media. They help greatly in closing 
the performance gap between processors and storage that we have seen widen in the last several decades. It will only be a 
matter of time before SSDs reach the same data density and cost per gigabyte of HDDs. \cite{Chen2016}

However, SSDs introduce new problems in applications due to the vastly different behaviors that they exhibit. Both software 
and hardware will need to start accommodating for these differences in order to reduce bottlenecks in data-intensive 
applications, such as database management systems. We have already seen this with the works in \cite{AppleComputer2017}, 
and more is sure to come.
